### 2017-11-17 manuscript.rmd
added code to make barplot/violinplot into manuscript

>>>>

######VARS data barplot code
```{r vars_plot, echo=F, message=F, warning=F}
#Get Raw Data
raw_data = read.csv(file="characer_coding/trim_siphdepths.tsv", sep = "\t")[,c(4,3,5:11)]
raw_data = raw_data[order(raw_data$ConceptName),]

#Clean Raw Data
names(raw_data)[1] = "Species"
raw_data$Species[which(raw_data$Species == "Kephyes")] = "Kephyes ovata"
raw_data$Species[which(raw_data$Species == "Lilyopsis")] = "Lilyopsis fluoracantha"
raw_data$Species[which(raw_data$Species == "Agalma")] = "Agalma elegans"
raw_data$Species[which(raw_data$Species == "Frillagalma")] = "Frillagalma vityazi"
raw_data$Species[which(raw_data$Species == "Stephalia")] = "Stephalia dilata"
raw_data$Species[which(raw_data$Species == "Lychnagalma")] = "Lychnagalma utricularia"
raw_data$Species[which(raw_data$Species == "Craseoa")] = "Craseoa lathetica"
raw_data$Species[which(raw_data$Species == "Cordagalma")] = "Cordagalma ordinatum"
raw_data$Species[which(raw_data$Species == "Desmophyes haematogaster")] = "Prayidae D27SS7"
raw_data$Species[which(raw_data$Species == "Craseoa lathetica")] = "Prayidae D27D2"

#Adjust Data to tree structure
raw_data[which(raw_data$Species %in% ultratree$tip.label),] -> intree_data
tree$tip.label[which(!(ultratree$tip.label %in% raw_data$Species))] %>% length() -> missSPP
missing_data_proxy <- raw_data[1:missSPP,]
missing_data_proxy$Species = ultratree$tip.label[which(!(ultratree$tip.label %in% raw_data$Species))]
missing_data_proxy$Depth = rep(20, missSPP)
parched_data <- rbind(missing_data_proxy, raw_data[which(raw_data$Species %in% ultratree$tip.label),])
parched_data = parched_data[which(!is.na(parched_data$Depth)),]
parched_data$Species <- factor(parched_data$Species, levels = ultratree$tip.label)

#Plots for FIGURE
ggplot(parched_data, aes(x = Species, y=-Depth)) + geom_boxplot() + theme_classic()
ggplot(parched_data, aes(x = Species, y=-Depth)) + geom_violin() + theme_classic()
